Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-04 papers/actus2021/article.tex
isda thoughts

>>>>

There are frameworks like ISDA Common Domain Model \cite{isda-cdm} providing 
more precise representation of business processes involved in institutional trading 
as well as code-generation capabilities. However, due to it's structural simplicity ACTUS 
is much more suited for generating code in a financial domain specific language 
like Marlowe rather than general-purpose one like Java or Haskell.
